### 2021-07-19 doc/thesis/chapters/system-design-process.tex
assess performance

>>>>

This step is all about measurements.
The performance of a system can only be evaluated, if it can be measured by using different metrics.
Evaluation criteria are used, based on the measurements of the technical performance, which can help to find trade-offs or to mitigate risk in design and manufacturing.
